IRTF Spectro-Photometry of Rotating Brown Dwarfs

### 2016-11-10 ms.tex
I wrote out the equations for the 2 temperature model.

\usepackage{natbib}
\usepackage[caption=false]{subfig}
\newcommand{\vdag}{(v)^\dagger}

@@

\citet{yang2015hstRotBD} also observe wavelength-dependent variability of 2MASS J1821 with the Hubble Space Telescope's (HST's) Wide Field Camera (WFC3) over 2 visits of 3 orbits each.
Their maximum over minimum flux spectrum is converted to an amplitude spectrum by assuming that the amplitude is half the difference in maximum and minimum flux, which can be shown to be 
\begin{equation}
A  = \frac{f_R - 1}{f_R + 1}
\end{equation}
where $f_R$ is the flux ratio of the maximum over minimum flux.

@@

@@

>>>>

\usepackage{natbib}
\usepackage[caption=false]{subfig}
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\degree}{$^\circ$}

@@

\citet{yang2015hstRotBD} also observe wavelength-dependent variability of 2MASS J1821 with the Hubble Space Telescope's (HST's) Wide Field Camera (WFC3) over 2 visits of 3 orbits each.
Their maximum over minimum flux spectrum is converted to an amplitude spectrum by assuming that the amplitude is half the difference in maximum and minimum flux, which can be shown to be 
\begin{equation}
A  = \frac{f_R - 1}{f_R + 1}
\end{equation}\label{eq:ampFromRatio}
where $f_R$ is the flux ratio of the maximum over minimum flux.

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.4\textwidth]{temperature_drawing.pdf}
\caption{A simple two layer model with two different temperatures and different areal fractions for longitudes 0\degree\ and 180\degree.}\label{fig:tdiffschem}
\end{centering}
\end{figure}

@@

I should change the spot model fit to the following model
\begin{equation}
f_{R,\lambda} = \frac{\alpha_1 B_\lambda(T_1) + (1-\alpha_1) B_\lambda(T_2)}{\alpha_2 B_\lambda(T_1) + (1-\alpha_2) B_\lambda(T_2)}
\end{equation}
where $\alpha_1$ and $\alpha_2$ are the areal fractions of the two temperature layers limited to [0,1], $B_\lambda$ is the Planck function, and $T_1$ and $T_2$ are the temperatures of the two levels.

Using equation \ref{eq:ampFromRatio}, the amplitude then becomes
\begin{equation}
A_\lambda = \frac{\left(\alpha_1 - \alpha_2 \right) \left(B_\lambda(T_1) - B_\lambda(T_2) \right)}{\left(\alpha_1 + \alpha_2\right) B_\lambda(T_1) + \left(2 - \alpha_1 - \alpha_2\right) B_\lambda(T_2)}.
\end{equation}
If the temperature difference is significant so that one Planck function is in the Wien's limit while the other is in the Rayleigh Jeans tail, the cooler temperature essentially becomes black and the contrast approaches a constant for short wavelengths.
